\let\cleardoublepage\clearpage
% Avoid empty page between appendix and references
\cleardoublepage
\addcontentsline{toc}{chapter}{Bibligraphy}
\bibliographystyle{alpha}

\begin{thebibliography}{1}
\vspace*{15pt}


\bibitem{art_perl} To Build Truly Intelligent Machines, Teach Them Cause and Effect {\em Quanta Magazine. Accessed:  \url{https://www.quantamagazine.org/to-buildtruly-intelligent-machines-teach-them-cause-and-effect-20180515}} July 2020.

\bibitem{ppc} RIP correlation. Introducing the Predictive Power Score {\em Florian Wetschoreck, Towards Data Science. Accessed:  \url{https://towardsdatascience.com/rip-correlation-introducing-the-predictive-power-score-3d90808b9598}} July 2020.

\bibitem{corr_trends} Correlation and dependence {\em Wikipedia, the free encyclopedia. Accessed:  \url{https://en.wikipedia.org/wiki/Correlation_and_dependence}} July 2020.

\bibitem{otto}  "Why Should I Trust You?" Explaining the Predictions of Any Classifier. {\em Marco Tulio Ribeiro, University of Washington et. al. Accessed:  \url{https://arxiv.org/pdf/1602.04938.pdf}} July 2020.

\bibitem{nove} Black-box vs. white-box models. {\em  Lars Hulstaert, Towards Data Science. Accessed:  \url{https://towardsdatascience.com/machine-learning-interpretability-techniques-662c723454f3}} July 2020.

\bibitem{causalens} Truly Explainable AI: Putting the “Cause” in “Because”. {\em  CausaLens. Accessed:  \url{https://media-exp1.licdn.com/dms/document/C4E1FAQFj_hm_0X1QlQ/feedshare-document-pdf-analyzed/0?e=1595084400&v=beta&t=zYhikB7P63ZSkJi2tTwGqxtM-SSlipOCF_6LZpgXUTU}} July 2020.

\bibitem{tools} The Seven Tools of Causal Inference with Reflections on Machine Learning. {\em JUDEA PEARL, UCLA Computer Science Department, USA. Accessed:  \url{https://ftp.cs.ucla.edu/pub/stat_ser/r481.pdf}} July 2020.

\bibitem{why} The Book of Why: The New Science of Cause and Effect. {\em Pearl, Judea and Mackenzie, Dana. Accessed:  \url{https://dl.acm.org/doi/book/10.5555/3238230}} July 2020.

\bibitem{system} Systems Thinking & Systems Modelling. {\em A Course for Understanding Systems and Creating Systems Models. The Sustainability Laboratory’s. Accessed:  \url{https://systemsinnovation.io/system-dynamics-book/}} July 2020.

\bibitem{cassie} Are you guilty of using the word “experiment” incorrectly?. {\em Cassie Kozyrkov - Towards Data Science. Accessed:  \url{https://towardsdatascience.com/are-you-guilty-of-using-the-word-experiment-incorrectly-9068baeab7a4}} July 2020.

\bibitem{eva} Causal Inference that’s not A/B Testing: Theory & Practical Guide. {\em Eva Gong - Towards Data Science. Accessed:  \url{https://towardsdatascience.com/causal-inference-thats-not-a-b-testing-theory-practical-guide-f3c824ac9ed2}} July 2020.

\bibitem{ml_peters} Elements of Causal Inference: Foundations and Learning Algorithms. {\em  Jonas Peters, Dominik Janzing et. al. The MIT Press. Accessed:  \url{https://mitpress.mit.edu/books/elements-causal-inference}} July 2020.

\bibitem{markov}
Introduction to Causal Inference
{\em Peter Spirtes, Department of Philosophy, Carnegie Mellon University. Accessed:  \url{http://www.jmlr.org/papers/volume11/spirtes10a/spirtes10a.pdf}} July 2020.

\bibitem{deep}
Causal Bayesian Networks: A flexible tool to enable fairer machine learning
{\em Silvia Chiappa and William Isaac, DeepMind. Accessed:  \url{https://deepmind.com/blog/article/Causal_Bayesian_Networks}} July 2020.

\bibitem{deep2}
Path-Specific Counterfactual Fairness
{\em Silvia Chiappa and Thomas P. S. Gillam, DeepMind. Accessed:  \url{https://arxiv.org/pdf/1802.08139.pdf}} July 2020.

\bibitem{six} CAUSALITY FOR MACHINE LEARNING. {\em Bernhard Schölkopf, Max Planck Institute for Intelligent Systems. Accessed:  \url{https://arxiv.org/pdf/1911.10500.pdf}} July 2020.

\bibitem{2minclass} 2 Minute Classroom {\em Endemic vs Epidemic vs Pandemic | How Epidemiologists Classify Disease Prevalence. Accessed:  \url{https://www.youtube.com/watch?v=nclAnJXdgqs}} June 2020.

\bibitem{exponentials} Exponential growth and epidemics {\em 3Blue1Brown. Accessed:  \url{https://www.youtube.com/watch?v=Kas0tIxDvrg}} June 2020.

\bibitem{physics} How To Tell If We're Beating COVID-19 {\em 
minutephysics. Accessed:  \url{https://www.youtube.com/watch?v=54XLXg4fYsc}} June 2020.

\bibitem{tds} Infectious Disease Modelling: Understanding the models that are used to model Coronavirus {\em Henri Froese, Towards Data Science. Accessed:  \url{https://www.youtube.com/watch?v=nclAnJXdgqs}} June 2020.

\bibitem{blob} Epidemic, Endemic, and Eradication Simulations {\em Primer. Accessed:  \url{https://www.youtube.com/watch?v=7OLpKqTriio}} June 2020.

\bibitem{immune} Modeling the Spreading of Diseases {\em Center for Biomedical Computing, Simula Research Laboratory, University of Oslo. Accessed:  \url{http://hplgit.github.io/disease-modeling/doc/pub/disease_modeling-beamer-red_shadow.pdf}} June 2020.

\bibitem{next} What Happens Next? COVID-19 Futures, Explained With Playable Simulations {\em It's Nicky!, Marcel Salathé & Nicky Case. Accessed:  \url{https://ncase.me/covid-19/}} June 2020.

\bibitem{pop_data} United Nations {\em Department of Economic and Social Affairs, World Population Prospects 2019. Accessed:  \url{https://population.un.org/wpp/DataQuery/}} June 2020.

\bibitem{beds_data} The World Bank Data {\em Hospital beds (per 1,000 people). Accessed:  \url{https://data.worldbank.org/indicator/SH.MED.BEDS.ZS}} June 2020.

\bibitem{cases_paper} ScienceMag.org {\em Substantial undocumented infection facilitates the rapid dissemination of novel coronavirus (SARS-CoV-2), Ruiyun Li et. al. Accessed:  \url{https://science.sciencemag.org/content/368/6490/489}} June 2020.

\bibitem{roche} The Centre for Evidence-Based Medicine develops, promotes and disseminates better evidence for healthcare. {\em COVID-19: Roche Antibody Test – 14th May.Susannah Fleming et. al. Accessed:  \url{https://www.cebm.net/covid-19/covid-19-roche-antibody-test-14th-may/}} June 2020.

\bibitem{pde} Oxford Mathematician explains SIR Travelling Wave Disease Model for COVID-19 (Coronavirus) {\em Tom Rocks Maths. Accessed:  \url{https://www.youtube.com/watch?v=uSLFudKBnBI&t=1s}} June 2020.

\bibitem{epic} Simulating an epidemic {\em 3Blue1Brown. Accessed:  \url{https://www.youtube.com/watch?v=gxAaO2rsdIs}} June 2020.

\bibitem{world_data} COVID-19 Data Repository by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University {\em CSSEGISandData, Accessed:  \url{https://github.com/CSSEGISandData/COVID-19}} June 2020.

\bibitem{news} Python News API {\em Accessed:  \url{https://newsapi.org/docs/get-started}} June 2020.

\bibitem{scott} Scott Ambler, Wikipedia {\em Accessed:  \url{https://en.wikipedia.org/wiki/Scott_Ambler}} July 2020.

\bibitem{sri_ex} What models can and cannot tell us about COVID-19. {\em Alexander F. Siegenfeld et. al. Accessed:  \url{https://www.pnas.org/content/pnas/early/2020/06/23/2011542117.full.pdf}} July 2020.

\bibitem{atom} COVID-19 dynamics with SIR model {\em The First Cry of Atom. Accessed:  \url{https://www.lewuathe.com/covid-19-dynamics-with-sir-model.html}} July 2020.

\bibitem{kutta} Programming for Computations – Python {\em Linge, H.P. Langtangen. Accessed:  \url{https://core.ac.uk/download/pdf/81856903.pdf}} July 2020.

\bibitem{darts} Time Series Made Easy in Python {\em Darts. Accessed:  \url{https://unit8co.github.io/darts/}} July 2020.

\bibitem{trials_data} COVID-19 Clinical Trials dataset {\em Parul Pandey, Kaggle.
Accessed:  \url{https://www.kaggle.com/parulpandey/covid19-clinical-trials-dataset}} July 2020.

\bibitem{power} Understanding Power Analysis in AB Testing {\em Paulynn Yu, Towards Data Science.
Accessed:  \url{https://towardsdatascience.com/understanding-power-analysis-in-ab-testing-14808e8a1554}} July 2020.

\bibitem{deaths_data} Conditions contributing to deaths involving coronavirus disease 2019 (COVID-19), by age group, United States. {\em 	National Center for Health Statistics. Accessed:  \url{https://data.cdc.gov/NCHS/Conditions-contributing-to-deaths-involving-corona/hk9y-quqm}} July 2020.

\bibitem{survival_an} Survival Analysis: Intuition & Implementation in Python. {\em 	Anurag Pandey, Towards Data Science. Accessed:  \url{https://towardsdatascience.com/survival-analysis-intuition-implementation-in-python-504fde4fcf8e}} July 2020.

\bibitem{surv1} Risk factors for severity and mortality in adult COVID-19 inpatients in Wuhan. {\em Xiaochen Li, MD et. al. Accessed:  \url{https://www.sciencedirect.com/science/article/pii/S0091674920304954}} July 2020.

\bibitem{surv2} Survival Analysis of COVID-19 on Democracy with Cox Proportional Hazards Model. {\em 	Yue Zhao and Deepika Dilip. Accessed:  \url{https://www.researchgate.net/publication/342228658_Survival_Analysis_of_COVID-19_on_Democracy_with_Cox_Proportional_Hazards_Model}} July 2020.

\bibitem{dowhy} DoWhy | Making causal inference easy. {\em 	Amit Sharma, Emre Kiciman - Microsoft. Accessed:  \url{https://microsoft.github.io/dowhy/}} July 2020.

\bibitem{causalml} Causal ML: A Python Package for Uplift Modeling and Causal Inference with ML. {\em UBER. Accessed:  \url{https://github.com/uber/causalml}} July 2020.

\bibitem{causalnex} CausalNex: A toolkit for causal reasoning with Bayesian Networks. {\em QuantumBlack. Accessed:  \url{https://github.com/quantumblacklabs/causalnex}} July 2020.

\bibitem{count_w} Doc Word Counter. {\em 	PDF - Word Counter, Counts the real number of words in any document format. Accessed:  \url{https://docwordcounter.com/en/PDF-word-counter}} July 2020.

\end{thebibliography}